\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-08 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
graph 2 and graph 3

\begin{figure}[htbp]
\caption{Trend in estimated transport costs (yearly mean value)}
\label{fig:Trends_in_TC}
\begin{center}
\includegraphics[width=14cm, height=7cm]{Figure2_Trend_of_totalTC_bymode.pdf}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Share of additive costs in total costs: Histogram}
\label{fig:histogram_beta}
\begin{center}
\begin{tabular}{cc}
%{\small (a) Air } & {\small (b) Vessel}\\
\includegraphics[width=3.0in, height=2.5in]{Etude_beta_pondere_air.pdf}
& \includegraphics[width=3.0in,height=2.5in]{Etude_beta_pondere_ves.pdf} \\
\multicolumn{2}{l}{{\footnotesize Notes: Distribution of $\beta_{ikt}$ over the triplet (year,product,country), weighted by share of yearly value of flow.}}\\
\end{tabular}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Trend in estimated transport costs (yearly mean value)}
\label{fig:Trends_in_TC}
\begin{center}
\includegraphics[width=14cm, height=7cm]{Figure2_Trend_of_totalTC_bymode.jpg}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Share of additive costs in total costs: Histogram}
\label{fig:histogram_beta}
\begin{center}
\begin{tabular}{cc}
%{\small (a) Air } & {\small (b) Vessel}\\
\includegraphics[width=3.0in, height=2.5in]{"Etude_beta_pondere_(a) Air transport".jpg}
& \includegraphics[width=3.0in,height=2.5in]{"Etude_beta_pondere_(b) Vessel transport".jpg} \\
\multicolumn{2}{l}{{\footnotesize Notes: Distribution of $\beta_{ikt}$ over the triplet (year,product,country), weighted by share of yearly value of flow.}}\\
\end{tabular}
\end{center}
\end{figure}
